Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-29 paper/paper.tex
not much committing because Im about to go to a meeting Tested everything on quipu.

The findings differ with Mannik's experimental findings
that show much less regular behavoir, with a large variation in the
location of maxima.  On the other hand, our stochastic simulations
show both robust pole to pole oscillations in the symmetric cells and
irregular behavoir in the assymetrical shapes, agreeing well with
Mannik's experimental findings.

>>>>

The results of these simulations differ significantly with Mannik's
experimental results that show much less regular behavoir, with a
large variation in the location of maxima.

On the other hand, our stochastic simulations show both robust pole to
pole oscillations in the symmetric cells and irregular behavoir in the
assymetrical shapes, agreeing well with Mannik's experimental
findings.
